---
title: "Daily Exercise 11 and 12: Building Linear Regression Models"
author: "Genesis Lacy, ESS 330 "
format: html
execute:
  echo: true
editor: visual
---

Part 1: Normality Testing

```{r}
library(tidyverse)
data("airquality")
str(airquality)
summary(airquality)

shapiro.test(airquality$Ozone)
shapiro.test(airquality$Solar.R)
shapiro.test(airquality$Wind)
shapiro.test(airquality$Temp)

```

The purpose of performing these tests is to see if the data we're using has a normal distribution.

Running the following code to see what our null and alternative hypotheses are:

```{r}
moments::agostino.test(na.omit(airquality$Ozone))

moments::agostino.test(na.omit(airquality$Solar.R))

moments::agostino.test(na.omit(airquality$Wind))

moments::agostino.test(na.omit(airquality$Temp))
```

Per the D'Agostino test that was just ran:

-   Ozone has a skewness of 1.2257 and there is an alt hypothesis. The p-value indicates that

-   Solar radiation has a skewness of -0.42363 and there is an alt hypothesis.

-   Wind has a skewness of 0.3444 and there is an alt hypothesis but this set of our data will have the most normality because the skewness is almost equal to 0.0.

-   Temperature has s skewness of -0.37417 and there is an alt hypothesis.

The p-values indicate that the data is \_\_\_\_ distributed.
